Title

### 2019-05-03 10_applications.tex
expand on litho section and TODOs

>>>>

\hl{The ambient illuminance can be better approximated using existing algorithms.
We can render the object lit from within and bake the illumination into a separate texture channel.
That channel can then serve as input to our program.}

Performing offsets can sometimes produce self-intersections.
We therefore export the outer and inner shell and perform a boolean difference operation using existing tools (Blender).
